A game of competition over risk

### 2023-04-21 paper/article.tex

\begin{result}
\label{res:scaling}
    When $C = \frac{1}{n^e}$ with $e \ge 0$, the efficiency $E = n w$ of the Nash equilibrium goes to $0$ if $e \le 1$ and it goes to $1$ if $e > 1$. We plot the behavior of $E$ in Figure \ref{fig:efficiency}.
\end{result}

We interpret Result \ref{res:scaling} as an indication that resources, here modeled by the ratio $\frac{1}{C} = \frac{R}{P}$ of rewards to penalties, need to scale faster than the number of players for them to adopt an efficient behavior. Scarcity of resources creates an inefficient Nash equilibrium.

>>>>

We observe that when $C = \frac{1}{n^e}$ with $e \ge 0$, the efficiency $E = n w$ of the Nash equilibrium goes to $0$ if $e \le 1$ and it goes to $1$ if $e > 1$. We plot the behavior of $E$ in Figure \ref{fig:efficiency}.
We interpret this as an indication that resources, here modeled by the ratio $\frac{1}{C} = \frac{R}{P}$ of rewards to penalties, need to scale faster than the number of players for them to adopt an efficient behavior. Scarcity of resources creates an inefficient Nash equilibrium.
